\textit{Supplemental materials for}: How is experience transformed into memory?

### 2018-09-04 paper/supplemental_materials.tex
backing up progress

\textbf{JRM STOPPED HERE}

\paragraph*{Distinctiveness.}
We also considered the distinctiveness of each recall event. That is, how uniquely a recall event matched a given video event compared to all other video events. We hypothesized that participants with high memory performance might describe each event in a more distinctive way (relative to those with lower memory performance who might describe events in a more general way). To this end, we computed a `distinctiveness' score for each participant (i.e., 1 - the correlation between a recall event and all non-matching video events).  Then, we averaged this measure over recall events within participant.  We found that participants with higher hand annotated memory performance also had higher distinctiveness scores (Pearson's $r(16) = 0.8, p = 0.0001$).

>>>>

\paragraph*{Distinctiveness.}
We also considered the \textit{distinctiveness} of each recalled event. That is, how uniquely a recalled event's topic vector matched a given video event topic vector, versus the topic vectors for the other video events.
\textbf{JRM STOPPED HERE}
We hypothesized that participants with high memory performance might describe each event in a more distinctive way (relative to those with lower memory performance who might describe events in a more general way). To this end, we computed a `distinctiveness' score for each participant (i.e., 1 - the correlation between a recall event and all non-matching video events).  Then, we averaged this measure over recall events within participant.  We found that participants with higher hand annotated memory performance also had higher distinctiveness scores (Pearson's $r(16) = 0.8, p = 0.0001$).
